\chapter{Introduction}
% Einleitung ist Kapitel 1
\label{kap:Einleitung} 

%---------------------------------------------------------------------------------------------------------
\section{Motivation}
When the integrated circuit was invented a possibility to reduce the size of digital circuits was born. Due to this the number of transistors per area increased and the prices for hardware decreased. In the last 20 to 30 years integrated circuits became part of nearly every electronic device, and life without it is not imaginable any more. Computers became effordable for all persons around the world. With shrinking sizes and lower power consumptions coming along, the ability to shrink whole computers to the size of one circuit board was achieved. Systems on chip (SoCs) were born.\\
Due to this it is implicapable that SoCs can be also used in small devices as well as in extraterritory satellites. As power is very much limited and every kilogram is very expensive to lift off from earth, a deeper view on those devices for using them in satellites should be done. Also the OPS-SAT mission uses a SoC as main processing unit. For this reason the possibilities of the used SoC and the programming capabilities should be analyzed.


%---------------------------------------------------------------------------------------------------------
\section{Purpose}
The purpose of this work is to investigate the possibilities of the used hardware and the programming capabilities of the used hardware in the OPS-SAT mission. It should be found out which possibilites modern hardware has, and which applications can be done. Some general hardware elements of which nearly every digital device exists are explained, as well as the functionality of the different parts of a SoC. Furthermore the way of programming hardware shall be mentioned.


%---------------------------------------------------------------------------------------------------------
\section{Structure}
The structure of this work is as follows:
\begin{itemize}
\item In chapter \ref{kap:Einleitung} some introduction is given. It is mentioned why this work was done and what the purpose of this project is.
\item In chapter \ref{kap:hardware} different types of integrated circuits are described. Furthermore some basic hardware elements which are needed to build digital hardware is mentioned. Those are amongst others possibilities of clock generation or flipflops.
\item Chapter \ref{kap:alteracyclone} contains useful information about the used Altera Cyclone V SoC. It is subdivided in a explanation of the used HPS and FPGA.
\item In chapter \ref{kap:HDL} the basic fundamentals of programming hardware is shown.
\item In Chapter \ref{kap:ausblick} applications of the system and some conclusion is given.
\end{itemize}